Collocation and keyword analysis on India-related text of *Natural History*

### 2023-08-27 paper_quarto.qmd
0827 final revise

In addition to the digitized textual content of *Natural History*, the place names mentioned in the text are annotated with their corresponding coordinates on TOPOXText. Since the annotations are available in an HTML format, they are scraped and restructured into a dataset of geographical-related text in *Natural History* with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python[^2]. The dataset structure, corpus scraping procedure and and corpus extension will be further explained in Corpus Description section (@sec-corpus).

@@

Based on this observation, the focus of the study is narrowed down to India-related texts in the *Natural History* to investigate what and how India is described in the work. By delving into the themes associated with the Indian region using the methods of collocation and keyword analysis, this study aims to examine Pliny the Elder's portrayal of India, which may shed light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.

@@

In this study, the **target corpus** includes all paragraphs in *Natural History* that mention place names in Indian regions, and the **reference corpus** includes all other paragraphs in the work. Lists of words with relatively higher frequency in the target corpus are obtained and sorted by the results of different measurements. The "keywords" found in the India-related text in *Natural History* provide more descriptive information about the topics and elements related to "India" in Pliny's narrative.

@@

@@

And the full text of the entire work, separated in paragraphs, are also scraped and stored in TXT format. Excluding those in target corpus, the other part of the work, containing `r length(fnames_wholetext_filtered)` files, serve as a **reference corpus**. The **reference corpus** contains `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.

@@

## Keyword in India-related text in *Natural History*

Additionally, in order to examine the significant phrases, i.e. "keyword", in the India-related content in the work, a keyword analysis for the India-related text is employed as a comparison and complement to the conclusion of the textual collocation analysis.

@@

Among the three lists sorted by different measures, 16/20 words of the absolute frequency top list overlap with that of the signed $G^2$ score. As shown in the @fig-col_keyword, the signed $G^2$ score has a positive correlation with the absolute frequency in this case.

@@

Moreover, since the PMI score indicates the degree of probability of the selected keyword's occurrence in the target corpus higher than that in the reference corpus, it could be a more convincing indicator for keyword analysis.

When checking the normalized frequency of the top 20 keywords with the most PMI score, as shown in @tbl-kw_frequency_pmi, almost all of them seem to be distinct in the India-related text, which reinforces the indication that they are especially key to the target corpus compared to the other parts of the work.

@@

These keywords were manually reviewed to determine their meaning and assigned classification tags based on their category. The explanations for the top 20 keywords with the highest PMI scores are displayed in the @tbl-kwlist below.

@@

Furthermore, a notable proportion of the keywords are place names, encompassing names of cities and islands in Indian subcontinent and neighboring areas.

To summarize, aside from echoing the focus on the geographical interconnection and the role as a trading hub related to India in the collocation analysis, the keyword analysis reveals two concrete themes, stones and rivers, in the narrative about India in *Natural History*. These themes provide additional information about the trading products and routes while also reflecting the transition of ancient Rome's geographical ideology from Greek.

@@

Moreover, the examination of keywords in India-related text aligns with the observations of the collocation analysis and highlights potential topics on stones and rivers about India in the work. These findings enhance the interpretation of the identified themes, such as geographical connectivity and merchandise trade, and also reflect Pliny's general geographical concern in the historical context of ancient Rome.

>>>>

In addition to the digitized textual content of *Natural History*, the place names mentioned in the text are annotated with their corresponding coordinates on TOPOSText. Since the annotations are available in an HTML format, they are scraped and restructured into a dataset of geographical-related text in *Natural History* with [Beautiful Soup](https://www.crummy.com/software/BeautifulSoup/bs4/doc/) library in Python[^2]. The dataset structure, corpus scraping procedure and and corpus extension will be further explained in Corpus Description section (@sec-corpus).

@@

Based on this observation, the focus of the study is narrowed down to India-related texts in the *Natural History* to investigate how India is described in the work. By delving into the themes associated with the Indian region using the methods of collocation and keyword analysis, this study aims to examine Pliny the Elder's portrayal of India, which may shed light on the spatial perception and imagination of the representative writers and scholars of ancient Rome.

@@

In this study, the **target corpus** includes all paragraphs in *Natural History* that mention place names in Indian regions, and the **reference corpus** includes all other paragraphs in the work. Lists of words with relatively higher frequency in the target corpus are obtained and sorted by the different measurements. The "keywords" found in the India-related text in *Natural History* provide more descriptive information about the topics and elements related to "India" in Pliny's narrative.

@@

# build frequency list for general corpus
flist_gen <- fnames_wholetext %>%
  freqlist(re_token_transf_in = "'", 
           token_transf_out = "")

@@

The full text of the entire work, separated in paragraphs, are also scraped and stored in TXT format as a **general corpus**. This **general corpus** of `r length(fnames_wholetext)` files contains `r prettyNum(n_tokens(flist_gen))` tokens and `r n_types(flist_gen)` types, with the type-token ratio of `r round(n_types(flist_gen)/n_tokens(flist_gen), 2)`.

Excluding those in target corpus from the general corpus, the other parts of the work contain `r length(fnames_wholetext_filtered)` files, serve as a **reference corpus**. The **reference corpus** contains `r prettyNum(n_tokens(flist_ref))` tokens and `r n_types(flist_ref)` types, with the type-token ratio of `r round(n_types(flist_ref)/n_tokens(flist_ref), 2)`.

The **general corpus** is employed for the collocation analysis and the **target corpus** and **reference corpus** are used in the keywords analysis.

@@

## Keywords in India-related text in *Natural History*

Additionally, in order to examine the significant phrases, i.e. "keywords", in the India-related content in the work, a keyword analysis for the India-related text is employed as a comparison and complement to the conclusion of the textual collocation analysis.

@@

Among the three lists sorted by different measures, 16/20 words of the absolute frequency top ranking list overlap with that of the signed $G^2$ score. As shown in the @fig-col_keyword, the signed $G^2$ score has a positive correlation with the absolute frequency in this case.

@@

Moreover, since the PMI score indicates the degree of probability of the selected keyword's occurrence in the target corpus higher than that in the reference corpus, it could be adopted as a more convincing indicator for keyword analysis.

When checking the normalized frequency of the top 20 keywords with the highest PMI score, as shown in @tbl-kw_frequency_pmi, almost all of them seem to be distinct in the India-related text, which reinforces the indication that they are especially key to the target corpus compared to the other parts of the work.

@@

These keywords are manually reviewed to determine their meaning and assigned classification tags based on their category. The explanations for the top 20 keywords with the highest PMI scores are displayed in the @tbl-kwlist below.

@@

Furthermore, a notable proportion of the keywords are place names, encompassing names of cities and islands in Indian subcontinent and its neighboring areas.

To summarize, aside from echoing the prominent themes about India found in the collocation analysis, the keyword analysis reveals two more concrete topics, namely stones and rivers, in the India-related narrative in *Natural History*. These topics provide additional information about the trading products and routes while also reflecting the transition of ancient Rome's geographical ideology from Greek.

@@

Moreover, the examination of keywords in India-related text aligns with the observations from the collocation analysis and highlights potential topics on stones and rivers about India in the work. These findings enhance the interpretation of the identified themes, such as geographical connectivity and merchandise trade, and also reflect Pliny's general geographical concern in the historical context of ancient Rome.
